Multifluid model of a one-dimensional steady state force-free current sheet

### 2024-07-22 index.qmd

---
title: "Multifluid model of a one-dimensional steady state force-free current sheet"
format:
  html: default
  pptx:
    slide-level: 3
    incremental: true
code-links:
  - text: Tana
    href: https://app.tana.inc?nodeid=OzzX0sVA4_6X
  - text: Zotero
    href: zotero://select/library/collections/DZHNUFNV
  - text: Overleaf
    href: https://www.overleaf.com/project/668273f5d14067a22517615c
abstract: "Solar wind plasma flow is characterized by intense, large-amplitude current sheets, also known as solar wind discontinuities. These regions are believed to play a crucial role in magnetic reconnection, solar wind ion heating, and energetic particle scattering. Although solar wind discontinuities share several properties with the classical MHD model of rotational discontinuities, they exhibit more complex characteristics that include many kinetic properties, going beyond this model. One of the most puzzling properties of these discontinuities is their Alvenicity, which describes the relationship between Alfvén and plasma velocity jumps across discontinuities. Although the high correlation of these jumps suggests the rotational nature of discontinuities, the significant differences in jump amplitudes indicate the necessity of kinetic mechanisms to describe the stress balance within discontinuities. Spacecraft observations show that plasma thermal anisotropy alone may not sufficiently explain this difference and achieve stress balance. In this study, we present a theoretical model in which this difference is explained by the kinetics of interpenetrating ion beams crossing the discontinuity. Our model successfully describes the observed properties of discontinuities within the inner heliosphere."
---

@@

The momentum equations (@eq-momentum) become:

$$
- u_1 \sin θ_1 θ_1' = n_1 u_1 \sin θ_1 B_z / Γ_1 - B_0 \sin θ
$$$$
\Rightarrow 
θ' = - \frac{n_1 B_z}{Γ_1} \pm \frac{B_0}{u_1}
$${#eq-theta1}

- Note that $θ_1, n_1$ are dependent variables, and $u_1, B_0, B_z, Γ_1$ are constants determined by the system.
- **Given $n_1$, we could solve $θ_1$ from the above equation.**
- The derivative of $θ$ goes to zero at infinity, gives us a relation between $u_1$ and $B_0$:

@@

## References

- @steinhauerMultifluidModelOnedimensional2008

>>>>

---
title: "Multifluid model of a one-dimensional steady state force-free current sheet"
format:
  html: default
  pptx:
    slide-level: 3
    incremental: true
code-links:
  - text: Tana
    href: https://app.tana.inc?nodeid=OzzX0sVA4_6X
  - text: Zotero
    href: zotero://select/library/collections/DZHNUFNV
---

@@

The first momentum equation (@eq-momentum) after substituting the above expression becomes:

$$
- u_α \sin θ_α θ_α' = n_α u_α \sin θ_α B_z / Γ_α - B_0 \sin θ
$$

$$
\Rightarrow 
θ_α' = - \frac{n_α B_z}{Γ_α} \pm \frac{B_0}{u_α}
$${#eq-theta1}

- Note that $θ_α, n_α$ are dependent variables, and $u_α, B_0, B_z, Γ_α$ are constants determined by the system.
- **So given the profile of $n_α$, we could solve the above equation to get the profile of $θ_α$, thus the profile of $u_α$.**
- The derivative of $θ$ goes to zero at infinity, gives us a relation between $u_1$ and $B_0$:

@@
